### 2018-11-06 document/manuscript.tex
Travis build: 55

We address questions like: - What is the publishing trend by Kenyan
researchers - Are they publishing open access, and how has this changed
over the years? - Are Kenyan researchers embracing pre-prints (BioRXiv,
AriRXiv, ResearchGate). Who is driving the adoption of pre-prints? Local
researchers or foreign collaborators? - What are the collaboration
trends? Are Kenyan researcher collaborating locally or internationally?

@@

This remains the main barrier to publishing open access, in addition to
the obsession with impact factors. However, for early career scientists
and students, especially in developing countries, most publishers offer
waivers and subsidies. In this section, we explore some of the avenues
to publishing open access at low cost.

To address this problem, we created a resource that can guide ECR and
students on where they publish open access, and at low cost. We also
provide information on how they can still be open, eg via the green
route.

@@

What is the take-home message from this article?

@@

We acknowledge the support from \ldots{} and the contribution from
\ldots{}.

>>>>

We address questions like: - What is the publishing trend by Kenyan
researchers - Are they publishing open access, and how has this changed
over the years? - Are Kenyan researchers embracing pre-prints (BioRXiv,
AriRXiv, ResearchGate, F1000Research). Who is driving the adoption of
pre-prints? Local researchers or foreign collaborators? - What are the
collaboration trends? Are Kenyan researcher collaborating locally or
internationally?

@@

The article processing charge is the main barrier to publishing open
access, in addition to the obsession with impact factors. However, for
early career scientists and students, especially in developing
countries, most publishers offer waivers and subsidies but few are
aware. In this section, we explore some of the avenues to publishing
open access at low cost.

To address this problem, we created a resource that can guide ECR and
students on where they publish open access, and at low cost. We also
provide information on how they can still be open when they publsih in
paywalled journals, eg via the green route.

@@

What is the take-home message from this article? What are the
recommendations?

@@

We acknowledge the support from \ldots{} and the contribution from
Mozilla Science Lab and KENET.
